Ab Initio Effective One-Electron Potentials Revisited: General Theory and Example Applications for Charge-Transfer Energy Calculations

### 2019-05-27 papers/2_oep_technique/paper-r0.tex
All 3 groups for CT-OEP energy added. Final working formula to be implemented added

As an illustration of application of the OEP technique for efficient calculation 
of CT energy we consider the second\hyp{}order perturbation theory of Murrell et al.,
in which the energy associated with the charge transfer from molecule $A$ to $B$ is given by
%
\begin{equation} \label{e:ct-murell-etal.e}
 E^{A\rightarrow B} = 2 \sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir} 
  \frac{\vert V^{A\rightarrow B}_{in} \vert^2 }{\varepsilon_i - \varepsilon_n}
\end{equation}
%
%coupling constants between occupied and virtual molecular orbitals 
%are re-expressed by the effective one-electron potentials. The resulting formula provides new possibilities 
%of optimization and applications in condensed phase simulations. [3]
%
where $\varepsilon_i$ and $\varepsilon_n$ are the canonical energies
of the occupied (denoted by `Occ') and virtual (denoted by `Vir') 
HF molecular orbitals, respectively,
whereas the coupling constant is given by
%
\begin{multline} \label{e:ct-murell-etal.vin}
 V^{A\rightarrow B}_{in} = 
        \tBraKet{i}{\hat{v}^B_{\rm ch} }{n} 
      - \sum_{j\in B}^{\rm Occ} \BraKet{nj}{ij} 
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} \\
      - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik} \;.
\end{multline}
%
In the above expression, the following effective potentials,
%
\begin{subequations} 
\begin{align} \label{e:ct-murell-etal.vtot-vi}
 \hat{v}^B_{\rm tot} &= \hat{v}^B_{\rm nuc} + 2\sum_{j\in B}^{\rm Occ} \hat{v}^B_{jj} \quad\text{ and }\\ 
 \hat{v}^A_{i      } &= \hat{v}^A_{\rm tot} - 2\hat{v}^A_{ii} \;,
\end{align}
\end{subequations}
%
were introduced without making any approximation to the original equation
from Ref. One can immediately notice that the five summation terms
from Eq.~\eqref{e:ct-murell-etal.vin} can be classified into three groups
regarding the type of ERI's that are required:
(i) $\BraKet{AB}{BB}$ -- the first two terms;
(ii) $\BraKet{AA}{BB}$ -- the third term and
(iii) $\BraKet{BB}{AA}$ -- the two last terms. 
%Note that groups (ii) and (iii) correspond to the Coulomb interactions between
%The group (i) corresponds to the overlap\hyp{}like integrals, whereas the groups (ii) and (iii)
%correspond to the Coulomb\hyp{}like integrals

\paragraph{Group (i).}
Group (i) can be rewritten by noticing that
%
\begin{equation} \label{e:ct-murell-etal.group-i.notice}
 \sum_{j\in B}^{\rm Occ} 
 \BraKet{nj}{ij} =
 \Bra{i} \left[ \hat{v}^B_{nj} \Ket{j} \right]  \;,
\end{equation}
%
which, by combining with the first term from Eq.~\eqref{e:ct-murell-etal.vin}, 
allows to apply the density fitting in an
incomplete basis set as follows
%
\begin{equation}
\Bra{i} \left[ \hat{v}^B_{\rm tot} \Ket{n} - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \Ket{j} \right]
\cong \Bra{i} \sum_{\eta\in B}^{\rm DF} V^B_{n\eta} \Ket{\eta}
\end{equation}
%
with the error density defined by
%
\begin{multline}
 \Xi_n({\bf r}) = 
  \left\{
      v_{nuc}^B({\bf r}) + 2 \sum_{j\in B}^{\rm Occ}
   \int \frac{ \vert \phi_j({\bf r}') \vert^2 }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
  \right\}
  \phi_n({{\bf r}})  \\
 - \sum_{j\in B}^{\rm Occ} \phi_j({{\bf r}})
   \int \frac{ \phi^*_n({\bf r}') \phi_j({{\bf r}'}) }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
 - \sum_{\eta\in B}^{\rm DF} V^B_{n\eta} \varphi_\eta({\bf r}) \;.
\end{multline}
%
Substituting the above equation into Eq.~\eqref{e:z-incompl}
%and then
%using resolution of identity to simplify the 
leads to
%
\begin{equation}
 V^B_{n\xi} = \sum_{\eta\in B}^{\rm DF} \left[ {\bf A}^{-1} \right]_{\xi\eta} b_\eta^{(n)} \;,
\end{equation}
%
where
%
\begin{multline}
 b^{(n)}_\eta = \iint 
           d{\bf r}_1 d{\bf r}_2  
           \frac{ \varphi^*_\eta({\bf r}_1) }
            {\vert {\bf r}_1 - {\bf r}_2 \vert } \\ \times
          \left[ 
           \hat{v}^B_{\rm tot}  \phi_n({\bf r}_2) 
         - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \phi_j({{\bf r}_2})
           \right]  \;.
\end{multline}
%
The above result is given by a sum of triple integrals from Eq.~\eqref{e:triple-integral}.
However, application of the resolution of identity as follows
%
\begin{equation}
 \hat{v}^B_{\rm tot} \Ket{n} - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \Ket{j}
 \cong \sum_{\varepsilon\in B}^{\rm RI} H_{n\varepsilon}^B \Ket{\varepsilon}
\end{equation}
%
leads to a much simpler formula
that requires only the one- and two\hyp{}electron integrals. 
Therefore, by combining
equations %which equations?
one arrives to
%
\begin{equation}
 V^B_{n\xi} = \sum_{\eta\in B}^{\rm DF} 
          \sum_{\varepsilon\in B}^{\rm RI}
         \left[ {\bf A}^{-1} \right]_{\xi\eta}
         H_{n\varepsilon}^B R_{\varepsilon \eta} \;,
\end{equation}
%
where
%
\begin{equation}
 H_{n\varepsilon}^B = \sum_{\eta\in B}^{\rm RI} \left[ {\bf S}^{-1} \right]_{\varepsilon\eta}
   a_\eta^{(n)}
\end{equation}
%
and
%%
\begin{align}
 a^{(n)}_\eta &= \tBraKet{\eta}{\hat{v}^B_{\rm tot}}{n}
      - \sum_{j\in B}^{\rm Occ} \tBraKet{\eta}{\hat{v}^B_{nj}}{j} \nonumber \\
 &= \sum_{y\in B} W^{(y)}_{\eta n} 
  + \sum_{j\in B}^{\rm Occ} 
  \left\{
   2\BraKet{\eta n}{jj} - \BraKet{\eta j}{nj} 
  \right\} \;.
\end{align}
%
Note that all the calculations that are required to obtain $V^B_{n\xi}$ are performed
solely on the densities and basis sets associated with the unperturbed molecule $B$.
Therefore, $V^B_{n\xi}$ can be considered as effective fragment parameters
used to compute the first two terms of Eq.~\eqref{e:ct-murell-etal.vin} by
%
\begin{equation}
        \tBraKet{i}{\hat{v}^B_{\rm ch} }{n} 
      - \sum_{j\in B}^{\rm Occ} \BraKet{nj}{ij} 
       = \sum_{\eta\in B}^{\rm RI} V^B_{n\eta} S_{\eta i} \;,
\end{equation}
%
which is a great simplification over the original form of group (i)
because only the overlap integrals between the $i$th MO on molecule $A$
and $\eta$th auxiliary orbital on molecule $B$ need to be evaluated on the fly.

\paragraph{Group (ii).}
The term belonging to this group can be considered as a sum of interaction
energies between the total charge density distribution of molecule $B$
and the partial density $\rho_{ik}({\bf r})$ of molecule $A$,
weighted by the overlap integrals $S_{nk}$. Using the distributed multipole 
expansion this can be written as
%
\begin{equation} \label{e:ct.group-2}
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} 
 \cong - \sum_{k\in A}^{\rm Occ} S_{nk} \rho_{ki}^A \odot \rho^B_{\rm tot} \;.
\end{equation}
%
Consider now a situation in which the localized occupied MO's are used.
If the multipole series expansions as truncated
at the distributed charges $q_i$ and dipole moments ${\BM{\upmu}_i}$, that are
located at the centroids ${\bf r}_i = \tBraKet{i}{\hat{\bf r}}{i}$, 
then the interaction energy can be written approximately as
%
\begin{multline}
 \rho_{ki}^A \odot \rho^B_{\rm tot} 
 \approx 
 q_{ki} 
 \left[
  %\sum_{i\in A}^{\rm LC} 
 \sum_{y\in B}^{\rm AT}
  \frac{Z_y}{\vert {\bf r}_y - {\bf r}_i \vert } 
 +
 \sum_{j\in B}^{\rm LC}
  \frac{q_j}{\vert {\bf r}_j - {\bf r}_i \vert } 
 \right] \\
 + \text{ dipole terms } \;.
\end{multline}
%
Note however that $q_{ik} = -\delta_{ik}$ and $q_j = -1$. Moreover, 
if the localized orbitals are perfectly spherical distributed dipole moments vanish.
This means that Eq.~\eqref{e:ct.group-2} can be approximated as follows
%
\begin{equation}
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} 
 \approx S_{ni}  \left[
  %\sum_{i\in A}^{\rm LC} 
 \sum_{y\in B}^{\rm AT}
  \frac{Z_y}{ r_{yi} } 
 -
 \sum_{j\in B}^{\rm LC}
  \frac{1}{r_{ji}} 
 \right] \;.
\end{equation}
%
Therefore, only overlap integrals are needed and relative distances between
atomic and LC's which leads to a great reduction of the evaluation cost
as compared to the original equation or the full multipole expansion.
We shall refer to this approximation as to
the spherical overlap approximation (SOA). Note that in order for this approximation to be valid,
occupied molecular orbitals need to be localized.

%If localized occupied MO's are used and only distributed charges ar, then $\rho_{ki} \approx \delta_{ki}$

\paragraph{Group (iii).}
\paragraph{Final OEP-based form of the coupling constant.}
Gathering the results from Eqs. the coupling constant
can be rewritten as follows
%
\begin{equation} \label{e:ct-murell-etal.vin.oep}
 V_{in}^{A\rightarrow B}
       = \sum_{\eta\in B}^{\rm RI} V^B_{n\eta} S_{\eta i} \;.
\end{equation}
%
Note that the only approximations made on it so fare was the application of density fitting
and resolution of identity. If the associated basis sets are sufficiently large, the errors
due to this approximation can be minimal and negligible.

%he above formula does not explicitly define an OEP due to the summation over different
%state vectors. 
%However, it can be achieved
%by transforming from MO to AO basis, i.e.,
%%
%\begin{equation}
% \hat{v}^B_{\rm tot} \Ket{n} - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \Ket{j}
% = \sum_{\beta\in B}^{\rm AO} 
% \left\{ 
%  C_{\beta n} \hat{v}^B_{\rm tot} - \sum_{j\in B}^{\rm Occ} C_{\beta j} \hat{v}^B_{nj} 
% \right\} \Ket{\beta} \;,
%\end{equation}
%%
%which leads to the OEP in spatial representation
%%
%\begin{multline}
% v_{\beta n}({\bf r}) \equiv C_{\beta n} v_{nuc}^B({\bf r}) \\ + 
%  \sum_{j\in B}^{\rm Occ} \Bigg\{ 
%   2 C_{\beta n} \int \frac{ \vert \phi_j({\bf r}') \vert^2 }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
% %\\
% - C_{\beta j} \int \frac{ \phi^*_n({\bf r}') \phi_j({\bf r}') }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
%  \Bigg\}  
%%
%\end{multline}
%%

@@

>>>>

As an illustration of application of the OEP technique for efficient calculation 
of CT energy we consider the second\hyp{}order perturbation theory of Murrell et al.,
in which the energy associated with the charge transfer from molecule $A$ to $B$ is given by
%
\begin{equation} \label{e:ct-murell-etal.e}
 E^{A\rightarrow B} = 2 \sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir} 
  \frac{\vert V^{A\rightarrow B}_{in} \vert^2 }{\varepsilon_i - \varepsilon_n}
\end{equation}
%
%coupling constants between occupied and virtual molecular orbitals 
%are re-expressed by the effective one-electron potentials. The resulting formula provides new possibilities 
%of optimization and applications in condensed phase simulations. [3]
%
where $\varepsilon_i$ and $\varepsilon_n$ are the canonical energies
of the occupied (denoted by `Occ') and virtual (denoted by `Vir') 
HF molecular orbitals, respectively,
whereas the coupling constant is given by
%
\begin{multline} \label{e:ct-murell-etal.vin}
 V^{A\rightarrow B}_{in} = 
        \tBraKet{i}{\hat{v}^B_{\rm tot} }{n} 
      - \sum_{j\in B}^{\rm Occ} \BraKet{nj}{ij} 
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} \\
      - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik} \;.
\end{multline}
%
In the above expression, the following effective potentials,
%
\begin{subequations} 
\begin{align} \label{e:ct-murell-etal.vtot-vi}
 \hat{v}^B_{\rm tot} &= \hat{v}^B_{\rm nuc} + 2\sum_{j\in B}^{\rm Occ} \hat{v}^B_{jj} \quad\text{ and }\\ 
 \hat{v}^A_{i      } &= \hat{v}^A_{\rm tot} - 2\hat{v}^A_{ii} \;,
\end{align}
\end{subequations}
%
were introduced without making any approximation to the original equation
from Ref. One can immediately notice that the five summation terms
from Eq.~\eqref{e:ct-murell-etal.vin} can be classified into three groups
regarding the type of ERI's that are required:
(i) $\BraKet{AB}{BB}$ -- the first two terms;
(ii) $\BraKet{AA}{BB}$ -- the third term and
(iii) $\BraKet{BB}{AA}$ -- the two last terms. 
%Note that groups (ii) and (iii) correspond to the Coulomb interactions between
%The group (i) corresponds to the overlap\hyp{}like integrals, whereas the groups (ii) and (iii)
%correspond to the Coulomb\hyp{}like integrals

\paragraph{Group (i).}
Group (i) can be rewritten by noticing that
%
\begin{equation} \label{e:ct-murell-etal.group-i.notice}
 \sum_{j\in B}^{\rm Occ} 
 \BraKet{nj}{ij} =
 \Bra{i} \left[ \hat{v}^B_{nj} \Ket{j} \right]  \;,
\end{equation}
%
which, by combining with the first term from Eq.~\eqref{e:ct-murell-etal.vin}, 
allows to apply the density fitting in an
incomplete basis set as follows
%
\begin{equation}
\Bra{i} \left[ \hat{v}^B_{\rm tot} \Ket{n} - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \Ket{j} \right]
\cong \Bra{i} \sum_{\eta\in B}^{\rm DF} V^B_{n\eta} \Ket{\eta}
\end{equation}
%
with the error density defined by
%
\begin{multline}
 \Xi_n({\bf r}) = 
  \left\{
      v_{nuc}^B({\bf r}) + 2 \sum_{j\in B}^{\rm Occ}
   \int \frac{ \vert \phi_j({\bf r}') \vert^2 }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
  \right\}
  \phi_n({{\bf r}})  \\
 - \sum_{j\in B}^{\rm Occ} \phi_j({{\bf r}})
   \int \frac{ \phi^*_n({\bf r}') \phi_j({{\bf r}'}) }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
 - \sum_{\eta\in B}^{\rm DF} V^B_{n\eta} \varphi_\eta({\bf r}) \;.
\end{multline}
%
Substituting the above equation into Eq.~\eqref{e:z-incompl}
%and then
%using resolution of identity to simplify the 
leads to
%
\begin{equation}
 V^B_{n\xi} = \sum_{\eta\in B}^{\rm DF} \left[ {\bf A}^{-1} \right]_{\xi\eta} b_\eta^{(n)} \;,
\end{equation}
%
where
%
\begin{multline}
 b^{(n)}_\eta = \iint 
           d{\bf r}_1 d{\bf r}_2  
           \frac{ \varphi^*_\eta({\bf r}_1) }
            {\vert {\bf r}_1 - {\bf r}_2 \vert } \\ \times
          \left[ 
           \hat{v}^B_{\rm tot}  \phi_n({\bf r}_2) 
         - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \phi_j({{\bf r}_2})
           \right]  \;.
\end{multline}
%
The above result is given by a sum of triple integrals from Eq.~\eqref{e:triple-integral}.
However, the following application of the resolution of identity,
%
\begin{equation}
 \hat{v}^B_{\rm tot} \Ket{n} - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \Ket{j}
 \cong \sum_{\varepsilon\in B}^{\rm RI} H_{n\varepsilon}^B \Ket{\varepsilon} \;,
\end{equation}
%
leads to a much simpler formula
that requires only the one- and two\hyp{}electron integrals. 
Therefore, by combining
equations %which equations?
one arrives to
%
\begin{equation}
 V^B_{n\xi} = \sum_{\eta\in B}^{\rm DF} 
          \sum_{\varepsilon\in B}^{\rm RI}
         \left[ {\bf A}^{-1} \right]_{\xi\eta}
         H_{n\varepsilon}^B R_{\varepsilon \eta} \;,
\end{equation}
%
where
%
\begin{equation}
 H_{n\varepsilon}^B = \sum_{\eta\in B}^{\rm RI} \left[ {\bf S}^{-1} \right]_{\varepsilon\eta}
   a_\eta^{(n)}
\end{equation}
%
and
%%
\begin{align}
 a^{(n)}_\eta &= \tBraKet{\eta}{\hat{v}^B_{\rm tot}}{n}
      - \sum_{j\in B}^{\rm Occ} \tBraKet{\eta}{\hat{v}^B_{nj}}{j} \nonumber \\
 &= \sum_{y\in B} W^{(y)}_{\eta n} 
  + \sum_{j\in B}^{\rm Occ} 
  \left\{
   2\BraKet{\eta n}{jj} - \BraKet{\eta j}{nj} 
  \right\} \;.
\end{align}
%
Note that all the calculations that are required to obtain $V^B_{n\xi}$ are performed
solely on the densities and basis sets associated with the unperturbed molecule $B$.
Therefore, $V^B_{n\xi}$ can be considered as effective fragment parameters
used to compute the first two terms of Eq.~\eqref{e:ct-murell-etal.vin} by
%
\begin{equation}
        \tBraKet{i}{\hat{v}^B_{\rm tot} }{n} 
      - \sum_{j\in B}^{\rm Occ} \BraKet{nj}{ij} 
       = \sum_{\eta\in B}^{\rm RI} V^B_{n\eta} S_{\eta i} \;,
\end{equation}
%
which is a great simplification over the original form of group (i)
because only the overlap integrals between the $i$th MO on molecule $A$
and $\eta$th auxiliary orbital on molecule $B$ need to be evaluated on the fly.
Note that the only approximation made so far was the application of density fitting
and resolution of identity. If the auxiliary and intermediate
basis sets are sufficiently large, the errors
due to this approximation can be minimal and negligible.

\paragraph{Group (ii).}
The term belonging to this group can be considered as a sum of interaction
energies between the total charge density distribution of molecule $B$
and the partial density $\rho_{ik}({\bf r})$ of molecule $A$,
weighted by the overlap integrals $S_{nk}$. Using the distributed multipole 
expansion this group can be written as
%
\begin{equation} \label{e:ct.group-2}
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} 
 \cong - \sum_{k\in A}^{\rm Occ} S_{nk} \rho_{ki}^A \odot \rho^B_{\rm tot} \;.
\end{equation}
%
Consider now a situation in which the localized occupied MO's are used.
If the multipole series expansions are truncated
at the distributed charges $q_i$ and dipole moments ${\BM{\upmu}_i}$, 
located at the centroids ${\bf r}_i = \tBraKet{i}{\hat{\bf r}}{i}$, 
then the interaction energy becomes
%
\begin{multline}
 \rho_{ki}^A \odot \rho^B_{\rm tot} 
 \approx 
 q_{ki} 
 \left[
  %\sum_{i\in A}^{\rm LC} 
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{\vert {\bf r}_y - {\bf r}_i \vert } 
 +
 2\sum_{j\in B}^{\rm LC}
  \frac{q_j}{\vert {\bf r}_j - {\bf r}_i \vert } 
 \right] \\
 + \text{ dipole terms } \;.
\end{multline}
%
Note however that $q_{ik} = -\delta_{ik}$ and $q_j = -1$. Moreover, 
if the localized orbitals are perfectly spherical distributed dipole moments vanish.
This means that Eq.~\eqref{e:ct.group-2} can be approximated as follows:
%
\begin{equation}
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} 
 \approx S_{ni}  \left[
  %\sum_{i\in A}^{\rm LC} 
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{ r_{yi} } 
 -
 \sum_{j\in B}^{\rm LC}
  \frac{2}{r_{ji}} 
 \right] \;.
\end{equation}
%
Therefore, only overlap integrals and relative distances between
atomic and LC's are needed, which leads to a great reduction of the
calculation cost,
as compared either to the original expression or to the multipole expansion (left\hyp{} and right\hyp{}hand sides
of Eq.~\eqref{e:ct.group-2}, respectively).
We shall refer to this approximation as to
the spherical overlap approximation (SOA). Note that in order for this approximation to be valid,
occupied molecular orbitals need to be localized.

\paragraph{Group (iii).}
The terms with the overlap integrals involving the occupied MO on $A$
can be combined into a single summation term, i.e.,
\begin{multline}
       - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik} \\ = -
 \sum_{k\in A}^{\rm Occ} 
 \sum_{j\in B}^{\rm Occ}
 S_{kj} 
 \tBraKet{j}{
 \underbrace{
 \left\{ 
  \delta_{ik} \left( \hat{v}^A_{k} + \hat{v}^A_{ik} \right)
  - \hat{v}^A_{ik}
 \right\} 
  }_{\hat{v}^{A,{\rm eff}}_{ik}}
 }{n}  \\ \cong -
%
  \sum_{k\in A}^{\rm Occ} 
 \sum_{j\in B}^{\rm Occ}
 S_{kj} 
 \rho_{nj}^B \odot \rho^{A,{\rm eff}}_{ik} \;,
\end{multline}
%
where the effective potential ${v}^{A,{\rm eff}}_{ik}$ (with the associated 
effective density $\rho^{A,{\rm eff}}_{ik}$) 
is defined by
%
\begin{equation}
 {v}^{A,{\rm eff}}_{ik}({\bf r}) \equiv
 \delta_{ik} 
 \left[
  v^A_{\rm tot} ({\bf r}) - 2 v^A_{k} ({\bf r}) + v^A_{ik} ({\bf r})
 \right] 
  - v^A_{ik} ({\bf r}) \;.
\end{equation}
%
Now, it is first assumed here that $\rho^{B}_{nj} ({\bf r}) \approx 0$ if occupied MO's on $B$ are localized.
This means that
%
\begin{multline}
        - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik}  \\
 \approx 0 \;.
\end{multline}
%
The above result is a crude approximation, since virtual MO's can overlap with occupied MO's to some extent.
In order to maintain $\rho^{B}_{nj}$ density, it is approximately represented here by a set of effective 
cumulative
atomic charges $\{ q^{B,(nj)}_{y} \}$ associated with the effective one\hyp{}particle density matrix
%
\begin{equation}
 D^{B,(nj)}_{\beta\delta} = C_{\beta n} C_{\delta j} \;.
\end{equation}
%
In this work, the effective charges were computed via the CAMM or ESP methods as
discussed in Section~XXX. Applying the SOA leads to 
%
\begin{multline}
        - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik}  \\
 \approx  -
 \sum_{j\in B}^{\rm Occ} S_{ij}
 \sum_{y\in B}^{\rm At} 
 q^{B,(nj)}_{y} 
 \left[ 
   \sum_{x\in A}^{\rm At}
   \frac{Z_x}{r_{xy}}
  + \frac{2}{r_{iy}}
  - \sum_{k\in A}^{\rm Occ}
    \frac{2}{r_{ky}} 
 \right]
 \;.
\end{multline}
%

\paragraph{Final OEP-based forms of the coupling constant.}
Gathering the results from Eqs. the coupling constant
can be given as follows
%
\begin{subequations}
\begin{align} \label{e:ct-murell-etal.vin.oep}
\Approx{ V_{in}^{A\rightarrow B} }{1}
       &= \sum_{\eta\in B}^{\rm RI} V^B_{n\eta} S_{\eta i} 
 +
S_{ni} u_i^{BA} \;, \\
%
\Approx{ V_{in}^{A\rightarrow B} }{2} &=
\Approx{ V_{in}^{A\rightarrow B} }{1} -
  \sum_{j   \in B}^{\rm Occ} S_{ij}
  \sum_{y   \in B}^{\rm At} q_y^{B,(nj)} w_{yi}^{BA}
\;,
\end{align}
\end{subequations}
%
where the auxiliary variables are
%
\begin{subequations}
\begin{align} \label{e:ct-murell-etal.vin.oep.aux-var}
 u_i^{BA} &\equiv    
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{ r_{yi} } 
 -
 \sum_{j\in B}^{\rm LC}
  \frac{2}{r_{ji}} 
                \;, \\
 w_{yi}^{BA} &\equiv 
   \sum_{x\in A}^{\rm At}
   \frac{Z_x}{r_{xy}}
  + \frac{2}{r_{iy}}
  - \sum_{k\in A}^{\rm Occ}
    \frac{2}{r_{ky}} 
                \;.
\end{align}
\end{subequations}
%
To compute the interaction energy due to CT from $A$ to $B$ by using the above SOA\hyp{}based
approximations, coupling elements need to be transformed from localized to canonical MO basis.
The final working formula reads
%
\begin{equation} \label{e:ect-oep.final}
 E^{A\rightarrow B} \approx
 2 
 \sum_{i\in A}^{\rm CMO}
 \sum_{n\in B}^{\rm Vir}
 \frac{
 \lvert
   \sum_{i'\in A}^{\rm LMO} L_{ii'}^A
   \Approx{V_{i'n}^{A\rightarrow B}}{} 
 \rvert^2 }{\varepsilon_i - \varepsilon_n} \;,
\end{equation}
%
where ${\bf L}^A$ is the CMO\hyp{}LMO transformation matrix for occupied orbitals of $A$. 
The total CT energy is given by the sum of the above contribution and the twin contribution
due to CT from $B$ to $A$.

%
%he above formula does not explicitly define an OEP due to the summation over different
%state vectors. 
%However, it can be achieved
%by transforming from MO to AO basis, i.e.,
%%
%\begin{equation}
% \hat{v}^B_{\rm tot} \Ket{n} - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \Ket{j}
% = \sum_{\beta\in B}^{\rm AO} 
% \left\{ 
%  C_{\beta n} \hat{v}^B_{\rm tot} - \sum_{j\in B}^{\rm Occ} C_{\beta j} \hat{v}^B_{nj} 
% \right\} \Ket{\beta} \;,
%\end{equation}
%%
%which leads to the OEP in spatial representation
%%
%\begin{multline}
% v_{\beta n}({\bf r}) \equiv C_{\beta n} v_{nuc}^B({\bf r}) \\ + 
%  \sum_{j\in B}^{\rm Occ} \Bigg\{ 
%   2 C_{\beta n} \int \frac{ \vert \phi_j({\bf r}') \vert^2 }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
% %\\
% - C_{\beta j} \int \frac{ \phi^*_n({\bf r}') \phi_j({\bf r}') }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
%  \Bigg\}  
%%
%\end{multline}
%%

@@

Bla.
